PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in RAMP PHQ data

## RAMP
```{r coping ramp phq cols}
if(RAMP == TRUE) {
coping.ramp.phq.raw <- readRDS(file = paste0(data.raw_path, "/ramp/phq_coping_ramp.rds"))
dim(coping.ramp.phq.raw)
colnames(coping.ramp.phq.raw)
}
```

```{r coping ramp phq summary labels}
if(RAMP == TRUE) {
summarytools::dfSummary(
  coping.ramp.phq.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
}
```

Will need to double check these namings once we have the new cleaned data -- KT. 
```{r coping ramp phq cleaning}
if(RAMP == TRUE) {
coping.ramp.phq.raw.id <- coping.ramp.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)
  ) %>%
  select(
    Sample, # Sample
    ID, # ID
    phq.problems_made_difficult_care,
    phq.pandemic_felt_feelings,
    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ RAMP prepandemic
    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ RAMP prepandemic
    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ RAMP prepandemic
    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ RAMP prepandemic
    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.ramp.phq.raw.id)
# Inspect colnames
colnames(coping.ramp.phq.raw.id)
#Differences
dim(coping.ramp.phq.raw)[1]-dim(coping.ramp.phq.raw.id)[1]
}
```

```{r coping ramp gad copy}
if(RAMP == TRUE) {
  coping.phq.raw.id <- coping.ramp.phq.raw.id
}
```

>>>>

## RAMP
```{r coping ramp phq cols}
if(RAMP == TRUE) {
ramp.phq.raw <- readRDS(file = paste0(data.raw_path, "/ramp/phq_ramp.rds"))
dim(ramp.phq.raw)
colnames(ramp.phq.raw)
}
```

```{r coping ramp phq summary labels}
if(RAMP == TRUE) {
summarytools::dfSummary(
  ramp.phq.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
}
```

Will need to double check these namings once we have the new cleaned data -- KT. 
```{r coping ramp phq cleaning}
if(RAMP == TRUE) {
ramp.phq.raw.id <- ramp.phq.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)
  ) %>%
  select(
    Sample, # Sample
    ID, # ID
    phq.problems_made_difficult_care = phq.issues_made_carrying_daily, #impact
    phq.pandemic_felt_feelings = phq.feelings_pandemic_felt, #before the pandemic question
    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things.1,
    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depression_or_hopeless, #THIS IS CORRECT - strange naming in raw dataset
    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble.1,
    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy.1,
    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating.1,
    phq.feeling_bad_failure_family_retro = phq.failure_family_feeling_bad.1,
    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading.1, 
    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly.1, 
    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts.1,
    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_base = phq.failure_family_feeling_bad,
    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading, # differ RAMP prepandemic
    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly, # differ RAMP prepandemic
    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(ramp.phq.raw.id)
# Inspect colnames
colnames(ramp.phq.raw.id)
#Differences
dim(ramp.phq.raw)[1]-dim(ramp.phq.raw.id)[1]
}
```

```{r coping ramp gad copy}
if(RAMP == TRUE) {
  coping.phq.raw.id <- ramp.phq.raw.id
}
```
